Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-06 tex/sections/apm.tex
Update blocks description
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Prover Machine gets as its primary input a vector $(\mathbf{C}_H,\mathbf{C}_P,\mathbf{C}_R)$, where
$\mathbf{C}_H$ is a commitment to the AscEE Heap, $\mathbf{C}_P$ is a commitment to the AscEE program area and
$\mathbf{C}_R$ is a commitment to an ordered list of requests. The APM then outputs the updated
commitments to the AscEE heap and program area and a final $\mathbf{accept}$ flag which indicates if the execution has
ended successfully or not: $(\mathbf{C}_{H'},\mathbf{C}_{P'},\mathbf{accept})$.

@@

The configuration of the APM can be considered as a quadruple
$(\mathbb{S},\mathbb{L},\mathbb{T}_{NEU},\mathbb{T}_{FRU})$,
where $\mathbb{S}$ is the size of the internal stack, $\mathbb{L}$ is the amount of local memory and
$\mathbb{T}_{NEU}, \mathbb{T}_{FRU}$ are the number of cycles that the Normal Execution Unit (NEU)
and Failure Repeater Unit (FRU) runs for. It should be noted that the APM has one local memory which
is used for all application calls.

>>>>

The Argennon Prover Machine gets as its primary input a vector $(\mathbf{C}_H,\mathbf{C}_P,\mathbf{C}_R)$ where
$\mathbf{C}_H$ is a commitment to the AscEE Heap, $\mathbf{C}_P$ is a commitment to the AscEE program area and
$\mathbf{C}_R$ is a commitment to an ordered list of requests. The APM then outputs the updated
commitments to the AscEE heap and program area and a final $\mathbf{accept}$ flag which indicates if the execution has
ended successfully or not: $(\mathbf{C}_{H'},\mathbf{C}_{P'},\mathbf{accept})$.

@@

The configuration of the APM can be considered as a tuple
\[
(\mathcal{S},\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}},\mathcal{T}_{\text{NEU}},
\mathcal{T}_{\text{FRU}})\ ,
\]
where $\mathcal{S}$ is the size of the internal stack, $\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}}$ are the
amount of local memory of the normal execution and failure repeater units respectively, and
$\mathcal{T}_{\text{NEU}},\mathcal{T}_{\text{FRU}}$ are the number of cycles that the NEU and FRU runs for. It should
be noted that the APM does not use a different local memory for each application call.

### 2022-09-06 tex/sections/blocks.tex
Fix some whitepaper typos
Update blocks description
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon blockchain is a sequence of blocks. Every block represents an ordered list of transactions, intended to be
executed by the Argennon Virtual Machine. The first block of the blockchain, the \emph{genesis} block, is a spacial
block that fully describes the initial state of the AVM. Every block of the Argennon blockchain thus corresponds to a
unique AVM state which can be calculated deterministically from the genesis block.

@@

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.5ex]
        \hline\hline
        commitment to the staking database            \\ [1.2ex]
        commitment to the method database             \\ [1.2ex]
        commitment to the heap database               \\ [1.2ex]
        commitment to the set of transactions         \\ [1.2ex]
        a consecutive list of block certificates issued     \\
        by validators' committee (if any)           \\ [1.2ex]
        clustering directives                         \\ [1.2ex]
        random seed                                   \\ [1.2ex]
        previous block hash                           \\ [1.2ex]
        \hline
    \end{tabular}
\end{center}

@@

Having the previous AVM state, the transaction list and the clustering directives of a block, a node can calculate
commitments to the staking, method and heap databases of the current block by emulating the AVM execution. If the
node can obtain the previous block commitments from a trusted source, it does not need to have a trusted local
copy of the AVM state,
and it can reliably retrieve the required storage pages from a ZK-EDB server. We call this type of block verification
\emph{conditional} block validation, since the validity of the current block is
conditioned on the validity of the previous block.

Interestingly, conditional block validation of multiple blocks can be done in parallel. If a node has enough bandwidth
and computational resources, it can conditionally verify any number of blocks from a previously created blockchain
simultaneously and in parallel. As we will see in Section~\ref{subsec:validators-committee}, this property plays an
important role in the Argennon consensus protocol.

To some extent, conditional validation of a single block could be parallelized as well. Many transactions
in a block are actually independent and the order of their execution does not
matter. These transactions can be safely validated in parallel. Section~\ref{sec:concurrency} further
develops this concept.

@@

An Argennon block certificate is an aggregate signature of some predefined subset of accounts. This predefined subset
is called the certificate committee and their signature ensures that the certified block is conditionally
valid given the validity of some previous block.

Argennon uses BLS aggregate signatures to represent block certificates. To better understand block certificates and
the Argennon consensus protocol, we need to briefly review the BLS signature scheme and its aggregation mechanism.

>>>>

The Argennon blockchain is a sequence of blocks. Every block represents an ordered list of external requests, intended
to be executed by the Argennon Smart Contract Execution Environment (AscEE). The first block of the blockchain, the
\emph{genesis} block, is a spacial block that fully describes the initial state of the AscEE. Every block of the
Argennon blockchain thus corresponds to a unique AscEE state which can be calculated deterministically from the genesis
block.

@@

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.6ex]
        \hline\hline
        height: $h$                          \\ [1.2ex]
        commitment to the program database: $\mathbf{C}_{P}$             \\ [1.2ex]
        commitment to the heap database: $\mathbf{C}_{H}$               \\ [1.2ex]
        commitment to the ordered list of requests: $\mathbf{C}_{R}$        \\ [1.2ex]
        clustering directives: $dir$                        \\ [1.2ex]
        certificate of the validators assembly for \\
        the block with height $h - k$: $v \mhyphen cert_{h-k}$         \\ [1.2ex]
        certificate of the delegates for\\
        the previous block: $d \mhyphen cert_{h-1}$        \\ [1.2ex]
        previous block hash                           \\ [1.2ex]
        \hline
    \end{tabular}
\end{center}

@@

To validate a block three main conditions need to be verified: (i) commitments to the program and heap
database result from applying the request list and clustering directives of the block to the previous AscEE
state, (ii) $v \mhyphen cert_{h-k}$ is valid, (iii) previous block is valid and has height $h - 1$.

We can denote condition (i) by a Computational Integrity (CI) statement:
\begin{equation}
    \label{eq:ci}
    \mathbf{C}_{P_h},\mathbf{C}_{H_h} \coloneqq \tau(\mathbf{C}_{P_{h-1}},\mathbf{C}_{H_{h-1}},\mathbf{C}_{R_{h}},
    dir_h)\ ,
\end{equation}
where $\tau$ is a transition function that encodes the AscEE computation logic and the necessary preprocessing and
postprocessing steps\footnote{including opening and updating the state commitments}.

Verifying statement~\ref{eq:ci} can be done by either replaying the AscEE computation and performing the required
preprocessing and postprocessing steps, or alternatively by
verifying a computation proof. To use computation proofs the verifier and prover need to share an arithmetized
representation of $\tau$ and use it for both proof generation and verification.

The Argennon Prover Machine provides a convenient and universal arithmetization for any Argennon
application. Moreover, since a compiled version of every Argennon application to the APM code is stored in the AscEE
program area, validators do not need to locally store the APM code of applications.

The Argennon protocol does not enforce the usage of the APM. Validators and PVC servers can use different methods
for arithmetization. This naturally would require that the ASAR of an application is used
for generating the appropriate arithmetization.

The certificate of validators, $v \mhyphen cert_{h-k}$, is an aggregate signature; validating it requires accessing the
AscEE heap state at block $h-k-1$ to obtain public keys and stake values. Again, in addition to direct verification,
a validator can use computation proofs, received from the Argennon cloud, to perform cheaper verification.

For validating the previous block, instead of directly validating the content of the block, a validator only
verifies the block certificates. Verifying $d \mhyphen cert_{h-1}$ is straightforward and verifying $v \mhyphen
cert_{h-1}$ can be cheaply done by using computation proofs, obtained from the Argennon cloud. This type of block
validation only validates the transition from block $h-1$ to block $h$, and the block is valid only if its previous
block is valid too. We
call this type of block verification \emph{conditional} block validation, since the validity of the current block is
conditioned on the validity of the previous block.

In summary, a validator validates a block by verifying three computation proofs: $\pi_{\tau}$ which proves the
transition is correct, $\pi_{h-k}$ which proves the validity of the included certificate of block $h-k$ and $\pi_{h-q}$
which proves the previous block has a correct certificate of validators. It should be noted that these proofs are not
a part of the block contents.

Interestingly, conditional block validation of multiple blocks can be done in parallel. Moreover, the required proofs
can be generated independently and by different PVC servers. As we will see in
Section~\ref{subsec:validators-committee}, this property plays an important role in the Argennon consensus protocol.

@@

An Argennon block certificate is an aggregate signature of some predefined subset of accounts. This predefined subset
is called the certificate assembly and their signature ensures that the certified block is conditionally
valid given the validity of some previous block.

Argennon uses a parallel algorithm to produce block certificates and therefore the signature scheme needs to satisfy
certain properties:
\begin{itemize}
    \item \textbf{Associative aggregation:} the signature aggregation operator is associative.
    \item \textbf{Efficient cancellation:} if $S$ is the predefined set of users that we need their aggregate
    signature, verifying an aggregate signature of $S-U$ can be done in time $O(T+|U|)$, where the aggregate
    signature of $S$ can be verified in
    $O(T)$.
\end{itemize}

An example for a signature scheme that supports all these properties is the BLS signature scheme.

\subsubsection{BLS Signatures}
